
\section{\bf Instructions for Software Documentation}

Each and every algorithm should be included in this software manual. Divide the
sections for the different competing methods for solving general problems. For
example, there should be a section for the Bisection method and Newton's method
in a section that addresses the general problem of finding roots for nonlinear
fnuctions of a single variable.

\vskip0.25in\hrule\vskip0.25in

\noindent {\bf Software Entries}

The following will be used in assessing the sections that document the various
codes written during the semester. You should take these as general guidelines
and if you have questions about the introduction to software manual ask your
instructor.

\begin{enumerate}
  \item The student demonsstrates a clear understanding of the general problem
        being solved by the algorithm represented by the code.
    \begin{enumerate}
      \item {\bf Not Addressed:} There is no discussion of the general problem
            or relationship to the algorithm that is represented by the computer
            code.
      \item {\bf Novice:}  There is a basic summary of the code and and a small
            number of comment lines embedded in the code.
      \item {\bf Intermediate:} The code representing the algorithm is well
            documented with the input and output variables clearly defined.
            There is little or no comparison to other methods or discussion
            about the limitations of the code you have written. The student does
            not include examples of how to use the code and verification of how
            how the code works on test problems.
      \item {\bf Expert:} The code is well documented with clear explanations of
            inputs and outputs. There is a discussion of how the algorithm works
            and verification that it works on examples. There is a discussion
            on how this code fits into the discussion of how to approximately
            solve the general problem with limitations on the code and
            algorithm.
    \end{enumerate}
\end{enumerate}

\noindent To get the highest possible grade aim for the expert level defined
above. Here again, I will grade on on how concise the descriptions are. Do not
include programs that call the software documented in these sections. Reserve
these until an appendix at the end of the software manual.

Also note that you will need to have a section for the basic methods you have
written for the class. For example, the routines that compute the vector norms
of arrays and such. These do not solve any general problems. However, they are
useful in many of the codes that you have written for the approximate solution
of a number of general problems. The basic methods as just described can be in
a section at the beginning or at the end or in an appendix.

\newpage
