\documentclass[11pt, oneside]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
								
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{setspace}
\onehalfspacing
\usepackage{fullpage}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsfonts,amsthm} % Math packages
\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
\newcommand{\R}{\Bbb{R}}
\newtheorem{thm}{Theorem}

\title{Exam 1 problems}
%\today

\begin{document}

\hrule

\noindent {\bf Introduction of Software Manual}

The following will be used in assessing the introduction to your software
manual. You should take these as general guidelines and if you have questions
about the introduction to software manual ask your instructor.

\begin{enumerate}
  \item The student demonsstrates a clear understanding of the content in the
        software manual.
    \begin{enumerate}
      \item {\bf Not Addressed:} There is no discussion of the organization of
            the software in the manual. There is no discussion of the purpose of
            the project or the software included in the manual.
      \item {\bf Novice:}  There is a basic summary of the content of the course
            in terms of various codes and routines that have been developed
            during the semester. Maybe something like a chapter by chapter
            summary of what is included in the chapter. No overall puspose for
            the project is included in the introduction.
      \item {\bf Intermediate:} Discussion of relationships between software in
            the various chapters is included in the introduction along with a
            brief summary of the purpose of the project is included.
      \item {\bf Expert:} Examples defining relationships bewtween chapters and
            software routines is included. A thorough discussion of the purpose
            of the project as it relates this and other classes and possible
            work is included in the introduction.
    \end{enumerate}
\end{enumerate}


\end{document}
